\chapter{Introduction}
Recommender systems are a natural response to the problem of information overload.

With a lot of information available a task does not necessarily get easier. When we need to make a choice when faced with complex information, we simplify it in order to better make sense of them and hasten decision-making. Recommender systems are a tool to solve that same common challenge for various domains. In philosophy, Thomas Hobbes argued that a social contract exists where people are willing to submit to the will of an outer authority out of self-interest and rationality, whether that authority is a dictator or elected assembly. They both serve the same purpose of making a choice on his behalf.\cite{Hobbes}

Today, machine learning makes informed choices on behalf of humans for their convenience, trading stocks or working various machine learning tasks. Humans are willingly trading decision power in return for the convenience. For a group of people putting aside their individual preferences in order to choose one among several items exists an unspoken social contract between them to accept the result of the process used to reach consensus. A group recommender could be the mainstay of this process, as it could reach a decision in the time it takes humans to pose the question. This motivates the need for a good recommender system.

Group recommender systems change the game and introduce new problems in the area of agreement. To avoid information overload, a group can defer to an outside authority to ease decision making, however doing so transfers problems from politics and ethics that are not easily answered. For a single user, the best choice in a recommendation is what will satisfy the user. However add more people and you get disagreement, meaning that some people's opinions are ignored. Kenneth J. Arrow proved this point back in 1948, that no aggregation method could possible ensure everyone was happy.

This ends out in that group recommendation's premiere problem being reconciling the differing opinions in the group in a manner that is both ethical and satisfactory for the group.

%However most of the research in the area has been for single user recommender systems, rather than for groups. The reason for this can be found in the evolution of the internet as a single user experience, which has lead to single user services, such as movie streaming services such as Netflix and Youtube, which are built around the idea of one person accessing their site at a time. The needs of such companies for powerful recommendation systems have pushed the envelope for recommender systems.
%Throughout time recommendations have often been a determined factor in decision making.
%The first recommendations were word-of-mouth recommendations where family and friends would proclaim their opinion about certain products like movies, books, or traveling destinations. 

%In the past decades the way we receive these recommendations have changed a lot. Today recommendations often occur online and there exist a recommender for almost every item or service available. The difference between these recommenders compared to word-of-mouth is that they are based on either what other people similar to you like or based on items similar to those associated with you, respectively collaborative or content-based recommendations.

%Even though recommenders is a big part of our everyday lives, there are some situations where there is a shortage in the recommender field. One of these shortcomings is group recommendation, like having a group of people deciding where to go on vacation, which movie to watch, or what music to hear. Some research have been done in the filed, but no method have yet been able to reflect the decision making process of a group. In this report we look into the problem of recommending to groups in order to obtain an acceptable level of satisfaction in the group.
\input{chapters/introduction/related_work}
\input{chapters/introduction/problem_areas}
\input{chapters/introduction/problem_statement}
\input{chapters/introduction/scenario}



%Start with hobbe's contract theory to argue for people giving up their freedom by choice to trust in laws and organizations
%Lead into history of recommendation and Kenneth J. Arrow
%Aggregation is imperfect - use as a quote
%as we don't have a ground truth, we'll need a new way to verify our recommender