\section{Group Recommendation}\label{sec:grouprecommendation}
This section documents the preprocessing done and outlines the rank aggregation methods used in order make the recommendation aggregation into a group recommendation. 
%In this section we explain the workings and concept behind the four aggregation methods.

\subsection{Preprocessing}
Prior to making the rank aggregation we do some preprocessing. As specified in Figure \ref{fig:composition} the preprocessing stages get groups and all the individual recommendations as input. Preprocessing is concerned with constructing a top-k list for each of the users in a specific group based on the individual recommendations.

A top-k list is specified as a ranked list of length $k$ consisting of the highest rated items order in descending order. More specifically let $\tau$ be a top-k list and let $\tau(i)$ be the rating of item $i$, which is an arbitrary item, then list is ranked if $\tau (1) > \tau (2) > ... > \tau (k)$.

The top-k lists are stored in a array which is used as input for the aggregation methods.

\subsection{Rank Aggregation}\label{sec:aggregations}
In this section we describe the aggregation methods. Common for all the aggregation methods is that they aggregate an array of top-k lists into one ranked list, $\omega$, of length $k$ containing recommendations of a group which is returned. The order of $\omega$ may differ between the methods as they rank it based on which items they deem most relevant for the group with the most relevant item first. 

\input{content/aggregations/bordacount}
\input{content/aggregations/markovchain}
\input{content/aggregations/spearmanfootrule}
\input{content/aggregations/average}